Local Group Satellite Distributions in the Illustris Simulation

### 2017-10-06 paper/paper.tex
updated plots in paper

\begin{figure*}
\centering
\includegraphics[width=0.40\textwidth]{LG_scatter_mu.pdf}
\includegraphics[width=0.40\textwidth]{LG_scatter_width.pdf}
\includegraphics[width=0.40\textwidth]{LG_scatter_ca_ratio.pdf}
\includegraphics[width=0.40\textwidth]{LG_scatter_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:lg_scatter}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.7\textwidth]{scatter_width.pdf}
\includegraphics[width=0.7\textwidth]{scatter_mu.pdf}
\includegraphics[width=0.7\textwidth]{scatter_ca_ratio.pdf}
\includegraphics[width=0.7\textwidth]{scatter_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:general}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.7\textwidth]{distribution_width.pdf}
\includegraphics[width=0.7\textwidth]{distribution_mu.pdf}
\includegraphics[width=0.7\textwidth]{distribution_ca_ratio.pdf}
\includegraphics[width=0.7\textwidth]{distribution_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:general}}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.35\textwidth]{LG_scatter_mu.pdf}
\includegraphics[width=0.35\textwidth]{LG_scatter_width.pdf}
\includegraphics[width=0.35\textwidth]{LG_scatter_ca_ratio.pdf}
\includegraphics[width=0.35\textwidth]{LG_scatter_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:lg_scatter}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.35\textwidth]{distribution_random_mu.pdf}
\includegraphics[width=0.35\textwidth]{distribution_random_width.pdf}
\includegraphics[width=0.35\textwidth]{distribution_random_ca_ratio.pdf}
\includegraphics[width=0.35\textwidth]{distribution_random_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:lg_distribution}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.7\textwidth]{scatter_mu.pdf}
\includegraphics[width=0.7\textwidth]{scatter_width.pdf}
\includegraphics[width=0.7\textwidth]{scatter_ca_ratio.pdf}
\includegraphics[width=0.7\textwidth]{scatter_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:general}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.7\textwidth]{distribution_mu.pdf}
\includegraphics[width=0.7\textwidth]{distribution_width.pdf}
\includegraphics[width=0.7\textwidth]{distribution_ca_ratio.pdf}
\includegraphics[width=0.7\textwidth]{distribution_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:general}}
\end{figure*}
